---
title: "Ageing hypothalamic astrocytes to separate nuclei transfer"
author: "Evgenii Tretiakov"
output: workflowr::wflow_html
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(
    autodep        = TRUE,
    cache          = FALSE,
    cache.lazy     = FALSE,
    dev            = c("png", "pdf"),
    echo           = TRUE,
    error          = FALSE,
    fig.align      = "center",
    fig.width      = 8,
    fig.asp        = 0.618,
    message        = FALSE,
    warning        = FALSE
)
# Load tidyverse infrastructure packages
suppressPackageStartupMessages({
  library(here)
  library(readr)
  library(purrr)
  library(dplyr)
  library(magrittr)
  library(stringr)
  library(skimr)
  library(future)
  library(kableExtra)
  library(reticulate)
})

reticulate::use_condaenv("/opt/python/3.8.8/bin/python")

# Load packages for scRNA-seq analysis and visualisation
suppressPackageStartupMessages({
  library(Seurat)
  library(SeuratWrappers)
  library(SeuratDisk)
  library(UpSetR)
  library(patchwork)
  library(swne)
  library(Nebulosa)
  library(Scillus)
  library(scCustomize)
  library(biomaRt)
  library(RobustRankAggreg)
})

# Set paths
raw_dir    <- here('../../data/PRJNA779749')
src_dir    <- here('code')
data_dir   <- here('data')
output_dir <- here('output')
plots_dir  <- here(output_dir, 'figures')
tables_dir <- here(output_dir, 'tables')
source(here(src_dir, 'functions.R'))
# source(here(src_dir, 'genes.R'))

# parallelisation
n_cores <- 20
plan("multiprocess", workers = n_cores)
options(future.globals.maxSize = 80000 * 1024^2) # 80Gb
# plan("sequential")
plan()

# set seed
reseed <- 42
set.seed(seed = reseed)

# ggplot2 theme
theme_set(ggmin::theme_powerpoint())

#' Save plot
save_my_plot <- function(name,
                         plt,
                         type,
                         h = 12,
                         asp = 1.618,
                         path = plots_dir,
                         format = ".pdf") {
  cowplot::save_plot(
    filename = here::here(
      path,
      stringr::str_glue(type,
        as.character(name),
        format,
        .sep = "_"
      )
    ),
    plot = plt,
    base_height = h,
    base_asp = asp,
    limitsize = FALSE
  )
}
```

```{r load-data}
genes.embed <- c("Ndrg2", "Slc1a3", "Gfap", 
                 "S100b", "Agt", "Slc6a11",
                 "Aqp4", "Nfia", "Aldoc", 
                 "Apoe", "Aldh1l1", "Sox9", 
                 "Fgfr3", "Egfr", "Ntrk2", "Gja1")
genes.nature <- c("Ndrg2", "Aqp4", "Gja1", 
                  "Slc17a9", "Slc17a7", "Slc17a6", 
                  "Slc16a1", "Slc16a7", "Slc16a3", 
                  "Panx1", "P2rx7", "Srr", 
                  "Dao", "Vamp2", "Gab1", 
                  "Slc18a1", "Slc18a2", "Slc18a3", 
                  "Slc17a5", "Osmr", "S100a6", 
                  "Ogn", "Itih5", "Rdh10", 
                  "Fst", "1500015O10Rik", "Rnf13", 
                  "A2m", "Rsph9", "Galnt16", 
                  "Rad23b", "Tgfbr2", "Ppp1r15a",
                  "Mlc1", "Slc6a11", "Slc1a3", "S100b",
                  "S100b", "Fabp7", "Gab1", "Igfbp5",
                  "Hopx", "Igsf1", "Tgfb2", "2810459M11Rik",
                  "Rnf13", "Itih5", "Slc1a2", "Cd59a",
                  "Vim", "Slc7a10", "Fos")

genes.jj <- c(
  "Acsbg1", "Acsl3", "Actb", "Agt", "Aldh1l1", "Aldoc", "Apoe",
  "Aqp4", "Atp1a2", "Bmpr1b", "Cbs", "Ckb", "Clu", "Cnx43",
  "Cpe", "Cst3", "Cth", "Cyp4f14", "Dbi", "Dbx2", "Dctd",
  "Dio2", "Ednrb", "Fgfr3", "Gabbr1", "Gabbr2", "Gjb6", "Gli3",
  "Gm266", "Gpr37l1", "Grhl1", "Grm3", "Gs", "Gucy2c", "Hapln1",
  "Hes5", "Heyl", "Hgf", "Id2", "Itih3", "Lars2", "Lcat",
  "Ldhb", "Malat1", "Mc3r", "Mfge8", "Mlc1", "Mmd2", "Mt1",
  "Mt2", "Ndrg2", "Nfia", "Npas3", "Nrxn1", "Ntrk2", "Ntsr2",
  "Olx1", "Otx2", "Pax6", "Pbxip1", "Phkg1", "Pla2g3", "Pla2g7",
  "Plcd4", "Plce1", "Plp1", "Ppap2b", "Ppia", "Prodh", "Ptprz1",
  "Rfx4", "Rpl41", "S1pr1", "Scd2", "Serpinb1c", "Slc19a3", "Slc1a2",
  "Slc1a3", "Slc39a12", "Slc4a4", "Slc6a11", "Son", "Sox2", "Sox9",
  "Sparc", "Sparcl1", "Tlr3"
)

genes.anatomy.jj <- c("Gfap", "Meg3", "Snhg11", "Ttc3", "Cst3", "Sparcl1",
                      "Ndrg2", "Cnx43", "Agt", "S100b", "Aldh1l1", "Lxn",
                      "Aqp4", "Slc1a2", "Fabp7", "Glul", "Olig2")

# public resources:
housekeeping_mouse <-
  read_lines(file = here(data_dir, 'housekeeping_mouse.tsv'))
astroenriched_mouse <-
  read_lines(file = here(data_dir, 'astrocyte_enriched_genes_shared_by_mice.tsv'))

astroprogenitor_humans <- 
  read_lines(file = here(data_dir, 'top_astrocytes_progenitor_cells_genes_by_humans.tsv')) |>
  str_to_sentence()
astromature_humans <-
  read_lines(file = here(data_dir, 'top_mature_astrocyte_genes_by_humans.tsv')) |>
  str_to_sentence()

# aggregate:
genes.manual <- unique(c(genes.embed, genes.nature,
                         genes.jj, genes.anatomy.jj,
                         astroenriched_mouse,
                         astromature_humans,
                         astroprogenitor_humans))

# ROC-test markers
srt.markers.roc <- read_csv(file = here(tables_dir,
                      'ageing_astr_recon-mrk_roc-sct.csv'))
srt.markers.roc %>%
    group_by(cluster) %>%
    slice_max(n = 3, order_by = avg_log2FC)

gene_list_plot <- 
  Extract_Top_Markers(marker_dataframe = srt.markers.roc,
                      num_genes = 3,
                      rank_by = "avg_log2FC",
                      make_unique = TRUE,
                      named_vector = FALSE)


# LR-test markers
srt.markers.lr <- read_csv(file = here(tables_dir,
                      'ageing_astr_recon-mrk_logreg-sct.csv'))
srt.markers.lr %>%
    group_by(cluster) %>%
    slice_max(n = 3, order_by = avg_log2FC)

gene_list_plot2 <- 
  Extract_Top_Markers(marker_dataframe = srt.markers.lr,
                      num_genes = 5,
                      rank_by = "avg_log2FC",
                      make_unique = TRUE,
                      named_vector = FALSE)

all_integrated <- LoadH5Seurat(here(raw_dir, "GSE188646-reintegrated.h5Seurat"))
astro <- LoadH5Seurat(here(raw_dir, "astro-wo-outliers.h5Seurat"))
```

```{r pl-all-integrated-whole-astrocytes-markers, fig.width=12, fig.asp=0.868}
DefaultAssay(object = all_integrated) <- "RNA"
plEmbCombWMrkR <- FeaturePlot(
  all_integrated,
  features = c("Fos", "Glul", "Gja1", "Ndrg2", 
               "S100b", "Tafa1", "Aldh1a1", "Plcb1", 
               "Sgcd", "Slit2", "Apoe", "Gfap", 
               "Slc38a1", "Cst3", "Lxn", "Mfn2"),
  min.cutoff = "q05", max.cutoff = "q95",
  ncol = 4, order = TRUE
) + patchwork::plot_annotation(title = "Astro-Marker choice (RNA)",
                               theme = theme(plot.title = element_text(size = 22)))
plEmbCombWMrkR

DefaultAssay(object = all_integrated) <- "integrated"
plEmbCombWMrkI <- FeaturePlot(
  all_integrated,
  features = c("Fos", "Glul", "Gja1", "Ndrg2", 
               "S100b", "Tafa1", "Aldh1a1", "Plcb1", 
               "Sgcd", "Slit2", "Apoe", "Gfap", 
               "Slc38a1", "Cst3", "Lxn", "Mfn2"),
  min.cutoff = "q05", max.cutoff = "q95",
  ncol = 4, order = TRUE
) + patchwork::plot_annotation(title = "Astro-Marker choice (integrated)",
                               theme = theme(plot.title = element_text(size = 22)))
plEmbCombWMrkI
save_my_plot(name = "ageing-pick-mrks-whole-integrated", 
             plt = plEmbCombWMrkI, 
             type = "feature-plot",
             h = 12,
             asp = 1.152)
```

```{r integration-features-astrocytes}
DefaultAssay(object = astro) <- "RNA"
subset_genes <- 
  astro@assays$RNA@counts |>
  rowSums(na.rm = TRUE) %>%
  .[. > 50 | . %in% genes.manual] %>% names() %>%
  .[!. %in% housekeeping_mouse]
astro <- DietSeurat(astro,
                    assays = "RNA",
                    features = subset_genes)
# select novoseq data only to avoid integration against multiple variables
astro <- 
  subset(astro, 
         subset = sample %in% c("Aged_3", "Aged_4",
                                "Young_3", "Young_4"))
astro@meta.data <- 
  astro@meta.data |> 
  dplyr::select(nCount_RNA, nFeature_RNA, stim, percent.mt, sample)
srt_list <- Seurat::SplitObject(astro, split.by = "sample")
srt_list <- lapply(X = srt_list,
                   vst.flavor = "v2",
                   FUN = SCTransform,
                   vars.to.regress = "percent.mt",
                   method = "glmGamPoi",
                   variable.features.n = 8000,
                   return.only.var.genes = FALSE,
                   seed.use = reseed,
                   verbose = FALSE)

features <- 
  SelectIntegrationFeatures(object.list = srt_list, 
                            nfeatures = 4000,
                            verbose = FALSE)
all_sct_features <- 
  srt_list |> 
  map(pluck, "assays", "SCT", "var.features") |>
  purrr::reduce(c) |> 
  unique()
keep_genes <- 
  c(genes.manual,
    features) |> 
  unique() %>%
  .[. %in% all_sct_features]
glimpse(keep_genes)

outOfAnchors <- keep_genes[!keep_genes %in% features]
cat(c("\n", outOfAnchors, "\n"))

CheckGenesInSCT <- function(gene) {
  srt_list |> 
    map(pluck, "assays", "SCT", "var.features") |> 
    map(~gene %in% .x) |> 
    simplify()
}
chkSamples <-
  outOfAnchors |>
  map(CheckGenesInSCT) |>
  base::simplify2array() |> 
  as_tibble()
colnames(chkSamples) <- outOfAnchors
chkSamples

selected_genes <-
  c(outOfAnchors[
    chkSamples |>
      map(all) |>
      simplify()],
    features)
glimpse(selected_genes)
```

```{r integration-object-astrocytes}
npcs <- 50
srt_list <-
  PrepSCTIntegration(object.list = srt_list,
                     anchor.features = selected_genes)

anchors <- FindIntegrationAnchors(
  object.list = srt_list,
  normalization.method = "SCT",
  anchor.features = selected_genes,
  reduction = "cca",
  dims = 1:npcs,
  k.anchor = 10,
  k.score = 50,
  k.filter = 100,
  max.features = 500,
  n.trees = 100,
  verbose = FALSE
)

combined_sct <- IntegrateData(
  anchorset = anchors,
  normalization.method = "SCT",
  features.to.integrate = selected_genes,
  dims = 1:npcs,
  k.weight = 200,
  verbose = FALSE
)

combined_sct <-
  RunPCA(combined_sct, npcs = npcs, 
         seed.use = reseed, verbose = FALSE)
combined_sct
```

```{r embed-integrated-ageing}
combined_sct <- combined_sct |> 
  RunUMAP(reduction = "pca", return.model = TRUE,
          densmap = TRUE, dims = 1:npcs, 
          seed.use = reseed, verbose = FALSE) |> 
  FindNeighbors(reduction = "pca", dims = 1:npcs, verbose = FALSE)
```

Plot by source

```{r pl-all-integrated-astrocytes-sample, fig.width=12, fig.asp=0.309}
plEmbCombBatch <- DimPlot(combined_sct, reduction = "umap",
                          group.by = "sample", pt.size = 5,
                          label = TRUE, repel = TRUE) + NoLegend()
plEmbCombReg <- DimPlot(combined_sct, reduction = "umap",
                        group.by = "stim", pt.size = 5,
                        label = TRUE, repel = TRUE) + NoLegend()
plEmbCombBatch + plEmbCombReg
```

```{r select-cells, fig.width=6}
# plot <- DimPlot(combined_sct, reduction = "umap")
# select.cells <- CellSelector(plot = plot)
if (!file.exists(here(data_dir,
         "outliers_webb_astrocytes.txt"))) {
  select.cells <-
    WhichCells(
      combined_sct, 
      expression = UMAP_1 > 5)
  write_lines(
    select.cells,
    here(data_dir,
         "outliers_webb_astrocytes.txt"))
} else {
  select.cells <- read_lines(
    here(data_dir,
         "outliers_webb_astrocytes.txt"))
}
Idents(combined_sct, cells = select.cells) <- "deleteme"
```

```{r check-outliers}
# Now, we find markers that are specific to the selected cells, and find clear duplets markers
combined_sct <-
  PrepSCTFindMarkers(combined_sct, assay = "SCT")
newcells.markers <-
  FindMarkers(
    combined_sct, 
    assay = "SCT",
    ident.1 = "deleteme",
    ident.2 = NULL,
    min.diff.pct = 0.3,
    only.pos = TRUE
  )
head(newcells.markers)

```

```{r pl-astro-integrated-contam-astrocytes-markers, fig.width=12, fig.asp=0.868}
FeaturePlot(
  combined_sct,
  features = c("Fos", "Glul", "Gja1", "Ndrg2", 
               "S100b", "Tafa1", "Aldh1a1", "Plcb1", 
               "Sgcd", "Slit2", "Apoe", "Gfap", 
               "Slc38a1", "Cst3", "Lxn", "Mfn2"),
  min.cutoff = "q05", max.cutoff = "q95",
  ncol = 4, pt.size = 5, order = TRUE
) + 
  patchwork::plot_annotation(
    title = "Astro-Marker choice (integrated astrocytes from novoseq)",
    theme = theme(plot.title = element_text(size = 22))
    )
```

```{r delete-outliers}
combined_sct2 <- subset(combined_sct, idents = c("deleteme"), invert = TRUE)
DimPlot(combined_sct2, label = T, repel = T, pt.size = 5, group.by = "sample")
DimPlot(combined_sct2, label = T, repel = T, pt.size = 5, group.by = "stim")

```

```{r delet-tmp-object}
combined_sct <- combined_sct2
rm(combined_sct2)
```

```{r rerun-integration-after-subset}
DefaultAssay(combined_sct) <- "RNA"
combined_sct <- DietSeurat(combined_sct, assays = "RNA")
srt_list <- 
  Seurat::SplitObject(combined_sct, split.by = "sample")
srt_list <- lapply(X = srt_list,
                   vst.flavor = "v2",
                   FUN = SCTransform,
                   vars.to.regress = "percent.mt",
                   method = "glmGamPoi",
                   variable.features.n = 8000,
                   return.only.var.genes = FALSE,
                   seed.use = reseed,
                   verbose = FALSE)

features <- 
  SelectIntegrationFeatures(object.list = srt_list, 
                            nfeatures = 4000,
                            verbose = FALSE)
all_sct_features <- 
  srt_list |> 
  map(pluck, "assays", "SCT", "var.features") |>
  purrr::reduce(c) |> 
  unique()
keep_genes <- 
  c(genes.manual,
    features) |> 
  unique() %>%
  .[. %in% all_sct_features]
glimpse(keep_genes)

outOfAnchors <- keep_genes[!keep_genes %in% features]
cat(c("\n", outOfAnchors, "\n"))

chkSamples <-
  outOfAnchors |>
  map(CheckGenesInSCT) |>
  base::simplify2array() |> 
  as_tibble()
colnames(chkSamples) <- outOfAnchors
chkSamples

selected_genes <-
  c(outOfAnchors[
    chkSamples |>
      map(all) |>
      simplify()],
    features)
glimpse(selected_genes)

npcs <- 50
srt_list <-
  PrepSCTIntegration(object.list = srt_list,
                     anchor.features = selected_genes)

anchors <- FindIntegrationAnchors(
  object.list = srt_list,
  normalization.method = "SCT",
  anchor.features = selected_genes,
  reduction = "cca",
  dims = 1:npcs,
  k.anchor = 10,
  k.score = 50,
  k.filter = 100,
  max.features = 500,
  n.trees = 100,
  verbose = FALSE
)

combined_sct <- IntegrateData(
  anchorset = anchors,
  normalization.method = "SCT",
  features.to.integrate = selected_genes,
  dims = 1:npcs,
  k.weight = 200,
  verbose = FALSE
)

```

```{r update-embedding}
npcs <- 50
combined_sct <- combined_sct |> 
  RunPCA(seed.use = reseed, verbose = FALSE) |> 
  RunUMAP(reduction = "pca", return.model = TRUE,
          densmap = TRUE, dims = 1:npcs, 
          seed.use = reseed, verbose = FALSE) |> 
  FindNeighbors(reduction = "pca", dims = 1:npcs, verbose = FALSE)
```

Plot by source after clean up

```{r pl-all-integrated-astrocytes-sample-clean, fig.width=12, fig.asp=0.309}
plEmbCombBatch <- DimPlot(combined_sct, reduction = "umap",
                          group.by = "sample", pt.size = 5,
                          label = TRUE, repel = TRUE) + NoLegend()
plEmbCombReg <- DimPlot(combined_sct, reduction = "umap",
                        group.by = "stim", pt.size = 5,
                        label = TRUE, repel = TRUE) + NoLegend()
plEmbCombBatch + plEmbCombReg
```

```{r pl-clustree, fig.width=10, fig.asp=1.618}
metadata <- combined_sct@meta.data
rownames(metadata) <- colnames(combined_sct)
ref.labels <- metadata$stim
library(mrtree)
resolutions <-
  modularity_event_sampling(
    A = combined_sct@graphs$integrated_snn,
    n.res = 15,
    gamma.min = 0.1,
    gamma.max = 2
  ) # sample based on the similarity matrix

# clustering using Suerat
combined_sct <- combined_sct |> 
  FindClusters(algorithm = 4, method = "igraph",
               resolution = resolutions, random.seed = reseed,
               verbose = FALSE)

# initial cluster tree from Seurat flat clustering
plot_clustree(
  labelmat = combined_sct@meta.data,
  prefix = 'integrated_snn_res.',
  ref.labels = ref.labels,
  plot.ref = FALSE
)
```

```{r pl-mrtree, fig.height=6, fig.width=11, echo=TRUE, include=FALSE}
out <-  mrtree(
  combined_sct,
  prefix = 'integrated_snn_res.',
  n.cores = n_cores,
  consensus = FALSE,
  augment.path = FALSE
)
# if there are few partitions per k, within resolution consensus step can speed up the algorithm
# weight per sample is encoraged if the classes are imbalanced

plot_tree(
  labelmat = out$labelmat.mrtree,
  ref.labels = ref.labels,
  plot.piechart = TRUE,
  node.size = 0.2,
  tip.label.dist = 10,
  bottom.margin = 30
)
```

```{r pl-clustering-amri}
# Adjusted Multiresolution Rand Index (AMRI)
ks.flat <-  apply(
  out$labelmat.flat,
  2,
  FUN = function(x)
    length(unique(x))
)
ks.mrtree <-  apply(
  out$labelmat.mrtree,
  2,
  FUN = function(x)
    length(unique(x))
)
amri.flat <-  sapply(1:ncol(out$labelmat.flat), function(i)
  AMRI(out$labelmat.flat[, i], ref.labels)$amri)
amri.flat <-  aggregate(amri.flat, by = list(k = ks.flat), FUN = mean)
amri.recon <-  sapply(1:ncol(out$labelmat.mrtree), function(i)
  AMRI(out$labelmat.mrtree[, i], ref.labels)$amri)

df <-  rbind(
  data.frame(
    k = amri.flat$k,
    amri = amri.flat$x,
    method = 'Seurat flat'
  ),
  data.frame(k = ks.mrtree, amri = amri.recon, method = 'MRtree')
)
ggplot2::ggplot(data = df, aes(x = k, y = amri, color = method)) + geom_line() + theme_bw()
```

```{r pl-clustering-resolution, fig.width=5}
stab.out <- stability_plot(out)
stab.out$plot
```

```{r select-resolution}
stab.out$df
resK <-
  stab.out$df |>
  as_tibble() |>
  filter(ari != 1) |> 
  top_n(n = 1, wt = ari) |> 
  purrr::pluck(1)
resK
table(as.factor(out$labelmat.mrtree[, sprintf("K%s",resK)]))
```

```{r pl-clustering, fig.height=5, fig.width=8}
combined_sct$k_tree <- as.factor(out$labelmat.mrtree[, sprintf("K%s",resK)])
p1 <- DimPlot(combined_sct, label = T, repel = T, pt.size = 5) + ggtitle("Unsupervised clustering") + NoLegend()
p2 <- DimPlot(combined_sct, label = T, repel = T, group.by = "k_tree", pt.size = 5) + ggtitle("MRTree") + NoLegend()

p1 | p2
```

```{r markers-tables}
Idents(combined_sct) <- "k_tree"
combined_sct <- 
  PrepSCTFindMarkers(combined_sct, assay = "SCT")

srt.markers.roc <- 
  FindAllMarkers(
    combined_sct,
    assay = "SCT",
    only.pos = TRUE,
    min.diff.pct = 0.1,
    logfc.threshold = 0.25,
    test.use = "roc")
write_csv(srt.markers.roc,
          here(tables_dir,
               'novoseq-ageing_astr_recon-fix-mrk_roc-sct.csv'))

srt.markers.roc %>%
    group_by(cluster) %>%
    slice_max(n = 3, order_by = avg_log2FC)


srt.markers.lr <-
  FindAllMarkers(
    combined_sct,
    assay = "SCT",
    only.pos = TRUE,
    min.diff.pct = 0.15,
    logfc.threshold = 0.25,
    test.use = "LR",
    latent.vars = "sample")
write_csv(srt.markers.lr,
          here(tables_dir,
               'novoseq-ageing_astr_recon-fix-mrk_logreg-sct.csv'))
srt.markers.lr %>%
    group_by(cluster) %>%
    slice_max(n = 3, order_by = avg_log2FC)


# srt.markers.mast <-
#   FindAllMarkers(
#     combined_sct,
#     assay = "SCT",
#     only.pos = TRUE,
#     min.diff.pct = 0.15,
#     logfc.threshold = 0.25,
#     test.use = "MAST",
#     latent.vars = c("sample", "percent.mt"))
# write_csv(srt.markers.mast,
#           here(tables_dir,
#                'novoseq-ageing_astr_recon-fix-mrk_mast-sct.csv'))
# srt.markers.mast %>%
#     group_by(cluster) %>%
#     slice_max(n = 3, order_by = avg_log2FC)

```

```{r pl-astro-integrated-filt-astrocytes-markers, fig.width=12, fig.asp=0.868}
FeaturePlot(
  combined_sct,
  features = c("Slc1a2", "Glul", "Gja1", "Ntrk2", 
               "S100b", "Tafa1", "Aldh1a1", "Aldh1l1",
               "Plcb1", "Slit2", "Apoe", "Gfap", 
               "Slc38a1", "Cst3", "Lxn", "Slc1a3", "Nfia"),
  min.cutoff = "q05", max.cutoff = "q95",
  ncol = 4, order = TRUE, pt.size = 5
) + 
  patchwork::plot_annotation(
    title = "Astro-Marker choice (integrated astrocytes from novoseq)",
    theme = theme(plot.title = element_text(size = 22))
    )
```

```{r load-astromap-by-nuclei, warning=FALSE}
hypoth.nuclei.astro <- LoadH5Seurat(file = here(data_dir, "comb_astrocytes.bak.h5Seurat"))
DefaultAssay(hypoth.nuclei.astro) <- "RNA"
hypoth.nuclei.astro <-
  hypoth.nuclei.astro |> 
  DietSeurat(assays = c("RNA"))
metadata <-
  hypoth.nuclei.astro@meta.data %>%
  dplyr::select(
    Dataset,
    Batch_ID,
    Cell_ID,
    SRA_ID,
    GEO_ID,
    Technology,
    Author_Region,
    Author_Exclude,
    Author_CellType,
    Sex,
    C185_named,
    C286_named,
    C465_named,
    nCount_RNA,
    nFeature_RNA,
    percent_mt
  )
rownames(metadata) <- colnames(hypoth.nuclei.astro)
hypoth.nuclei.astro@meta.data <- metadata
hypoth.list <-
  Seurat::SplitObject(
    hypoth.nuclei.astro,
    split.by = "Batch_ID")

n_pcs <- 30

if (!file.exists(
  here(data_dir,
       "astrocytes-srt_by_nuclei.rds"))) {
  hypoth.list <- lapply(X = hypoth.list,
                        FUN = DeriveKTree,
                        n.pcs = n_pcs,
                        vseed = reseed,
                        n.cores = n_cores)
  hypoth.list[["Lopez_2021_10xv3"]] <-
    LoadH5Seurat(
      file = here("../../data/PRJNA679294",
                  "astrocytes.h5Seurat"))
  write_rds(hypoth.list,
            here(data_dir,
                 "astrocytes-srt_by_nuclei.rds"))
} else {
  hypoth.list <-
    read_rds(here(data_dir,
                  "astrocytes-srt_by_nuclei.rds"))
}

plan("multiprocess", workers = n_cores)
features.list <-
  hypoth.list %>%
  map(~SelectIntegrationFeatures(object.list = append(srt_list, .x),
                                 nfeatures = 5000))
write_rds(
  features.list,
  here(data_dir,
       "integration_features_by_nuclei.rds"))
```

## Arcuate nucleus

### Campbell et al. 2017 Dropseq

```{r transfer-ageing-campbell-2017-1}
hypoth.query.campbell_2017.1 <-
  hypoth.list[["CampbellDropseq_batch_1"]]
hypoth.anchors.campbell_2017.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.campbell_2017.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.campbell_2017.1 <-
  TransferData(
    anchorset = hypoth.anchors.campbell_2017.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.campbell_2017.1 <-
  MapQuery(
    anchorset = hypoth.anchors.campbell_2017.1,
    reference = combined_sct,
    query = hypoth.query.campbell_2017.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.campbell_2017.1, filename = here(data_dir, "hypoth.query.campbell_2017.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-campbell-2017-1-ageing}
campbell_2017.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.campbell_2017.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

campbell_2017.1.predictions.hypoth <-
  TransferData(
    anchorset = campbell_2017.1.anchors.hypoth,
    reference = hypoth.query.campbell_2017.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = campbell_2017.1.anchors.hypoth,
    reference = hypoth.query.campbell_2017.1,
    query = combined_sct,
    refdata = list(arc_campbell_2017_1_mrt = "k_tree"),
    new.reduction.name = "campbell2017.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-campbell-2017-1}
p1 <-
  DimPlot(
    combined_sct,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference annotations")

p.campbell_2017.1 <-
  DimPlot(
    hypoth.query.campbell_2017.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Campbell et al. 2017 batch-1 transferred labels")

p1 + p.campbell_2017.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-campbell-2017-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.campbell_2017.1 <-
  DimPlot(
    hypoth.query.campbell_2017.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Campbell et al. 2017 batch-1 transferred labels")

p.orig.campbell_2017.1 <-
  DimPlot(
    hypoth.query.campbell_2017.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) + 
  NoLegend() +
  ggtitle("Campbell et al. 2017 batch-1 annotations")

p.campbell_2017.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "campbell2017.1.umap",
    group.by = "predicted.arc_campbell_2017_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Campbell et al. 2017 batch-1")

p.hypoth.campbell_2017.1 +
  p.orig.campbell_2017.1 + 
  p.campbell_2017.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.campbell_2017.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "campbell2017.1.umap")[,"campbell20171umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.campbell_2017.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "campbell2017.1.umap")[,"campbell20171umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.campbell_2017.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "campbell2017.1.umap")[,"campbell20171umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.campbell_2017.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "campbell2017.1.umap")[,"campbell20171umap_2"])))
    )
  )
```

### Lutomska et al. 2022 10xV3

```{r transfer-ageing-lutomska-2022-1}
hypoth.query.lutomska_2022.1 <-
  hypoth.list[["Lutomska_chow_10xv3"]]
hypoth.anchors.lutomska_2022.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.lutomska_2022.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.lutomska_2022.1 <-
  TransferData(
    anchorset = hypoth.anchors.lutomska_2022.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.lutomska_2022.1 <-
  MapQuery(
    anchorset = hypoth.anchors.lutomska_2022.1,
    reference = combined_sct,
    query = hypoth.query.lutomska_2022.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.lutomska_2022.1, filename = here(data_dir, "hypoth.query.lutomska_2022.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-lutomska-2022-1-ageing}
lutomska_2022.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.lutomska_2022.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

lutomska_2022.1.predictions.hypoth <-
  TransferData(
    anchorset = lutomska_2022.1.anchors.hypoth,
    reference = hypoth.query.lutomska_2022.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = lutomska_2022.1.anchors.hypoth,
    reference = hypoth.query.lutomska_2022.1,
    query = combined_sct,
    refdata = list(arc_lutomska_2022_1_mrt = "k_tree"),
    new.reduction.name = "lutomska2022.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-lutomska-2022-1}
p.lutomska_2022.1 <-
  DimPlot(
    hypoth.query.lutomska_2022.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Lutomska et al. 2022 batch-1 transferred labels")

p1 + p.lutomska_2022.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-lutomska-2022-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.lutomska_2022.1 <-
  DimPlot(
    hypoth.query.lutomska_2022.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Lutomska et al. 2022 batch-1 transferred labels")

p.orig.lutomska_2022.1 <-
  DimPlot(
    hypoth.query.lutomska_2022.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Lutomska et al. 2022 batch-1 annotations")

p.lutomska_2022.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "lutomska2022.1.umap",
    group.by = "predicted.arc_lutomska_2022_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Lutomska et al. 2022 batch-1")

p.hypoth.lutomska_2022.1 +
  p.orig.lutomska_2022.1 +
  p.lutomska_2022.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.lutomska_2022.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "lutomska2022.1.umap")[,"lutomska20221umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.lutomska_2022.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "lutomska2022.1.umap")[,"lutomska20221umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.lutomska_2022.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "lutomska2022.1.umap")[,"lutomska20221umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.lutomska_2022.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "lutomska2022.1.umap")[,"lutomska20221umap_2"])))
    )
  )
```

### Deng et al. 2021 10xV3

```{r transfer-ageing-deng-2021-1}
hypoth.query.deng_2021.1 <-
  hypoth.list[["Deng10xv3_536-1_chow-diet"]]
hypoth.anchors.deng_2021.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.deng_2021.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.deng_2021.1 <-
  TransferData(
    anchorset = hypoth.anchors.deng_2021.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.deng_2021.1 <-
  MapQuery(
    anchorset = hypoth.anchors.deng_2021.1,
    reference = combined_sct,
    query = hypoth.query.deng_2021.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.deng_2021.1, filename = here(data_dir, "hypoth.query.deng_2021.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-deng-2021-1-ageing}
deng_2021.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.deng_2021.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

deng_2021.1.predictions.hypoth <-
  TransferData(
    anchorset = deng_2021.1.anchors.hypoth,
    reference = hypoth.query.deng_2021.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = deng_2021.1.anchors.hypoth,
    reference = hypoth.query.deng_2021.1,
    query = combined_sct,
    refdata = list(arc_deng_2021_1_mrt = "k_tree"),
    new.reduction.name = "deng2021.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-deng-2021-1}
p.deng_2021.1 <-
  DimPlot(
    hypoth.query.deng_2021.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-1 transferred labels")

p1 + p.deng_2021.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-deng-2021-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.deng_2021.1 <-
  DimPlot(
    hypoth.query.deng_2021.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-1 transferred labels")

p.orig.deng_2021.1 <-
  DimPlot(
    hypoth.query.deng_2021.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-1 annotations")

p.deng_2021.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "deng2021.1.umap",
    group.by = "predicted.arc_deng_2021_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Deng et al. 2021 batch-1")

p.hypoth.deng_2021.1 +
  p.orig.deng_2021.1 +
  p.deng_2021.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.deng_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "deng2021.1.umap")[,"deng20211umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.deng_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "deng2021.1.umap")[,"deng20211umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.deng_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "deng2021.1.umap")[,"deng20211umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.deng_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "deng2021.1.umap")[,"deng20211umap_2"])))
    )
  )
```

```{r transfer-ageing-deng-2021-3}
hypoth.query.deng_2021.3 <-
  hypoth.list[["Deng10xv3_536-3_chow-diet"]]
hypoth.anchors.deng_2021.3 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.deng_2021.3,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.deng_2021.3 <-
  TransferData(
    anchorset = hypoth.anchors.deng_2021.3,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.deng_2021.3 <-
  MapQuery(
    anchorset = hypoth.anchors.deng_2021.3,
    reference = combined_sct,
    query = hypoth.query.deng_2021.3,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.deng_2021.3, filename = here(data_dir, "hypoth.query.deng_2021.3.h5Seurat"), overwrite = TRUE)
```

```{r transfer-deng-2021-3-ageing}
deng_2021.3.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.deng_2021.3,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

deng_2021.3.predictions.hypoth <-
  TransferData(
    anchorset = deng_2021.3.anchors.hypoth,
    reference = hypoth.query.deng_2021.3,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = deng_2021.3.anchors.hypoth,
    reference = hypoth.query.deng_2021.3,
    query = combined_sct,
    refdata = list(arc_deng_2021_3_mrt = "k_tree"),
    new.reduction.name = "deng2021.3.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-deng-2021-3}
p.deng_2021.3 <-
  DimPlot(
    hypoth.query.deng_2021.3,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-3 transferred labels")

p1 + p.deng_2021.3 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-deng-2021-3-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.deng_2021.3 <-
  DimPlot(
    hypoth.query.deng_2021.3,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-3 transferred labels")

p.orig.deng_2021.3 <-
  DimPlot(
    hypoth.query.deng_2021.3,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-3 annotations")

p.deng_2021.3.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "deng2021.3.umap",
    group.by = "predicted.arc_deng_2021_3_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Deng et al. 2021 batch-3")

p.hypoth.deng_2021.3 +
  p.orig.deng_2021.3 +
  p.deng_2021.3.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.deng_2021.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "deng2021.3.umap")[,"deng20213umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.deng_2021.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "deng2021.3.umap")[,"deng20213umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.deng_2021.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "deng2021.3.umap")[,"deng20213umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.deng_2021.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "deng2021.3.umap")[,"deng20213umap_2"])))
    )
  )
```

```{r transfer-ageing-deng-2021-5}
hypoth.query.deng_2021.5 <-
  hypoth.list[["Deng10xv3_536-5_chow-diet"]]
hypoth.anchors.deng_2021.5 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.deng_2021.5,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.deng_2021.5 <-
  TransferData(
    anchorset = hypoth.anchors.deng_2021.5,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.deng_2021.5 <-
  MapQuery(
    anchorset = hypoth.anchors.deng_2021.5,
    reference = combined_sct,
    query = hypoth.query.deng_2021.5,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.deng_2021.5, filename = here(data_dir, "hypoth.query.deng_2021.5.h5Seurat"), overwrite = TRUE)
```

```{r transfer-deng-2021-5-ageing}
deng_2021.5.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.deng_2021.5,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

deng_2021.5.predictions.hypoth <-
  TransferData(
    anchorset = deng_2021.5.anchors.hypoth,
    reference = hypoth.query.deng_2021.5,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = deng_2021.5.anchors.hypoth,
    reference = hypoth.query.deng_2021.5,
    query = combined_sct,
    refdata = list(arc_deng_2021_5_mrt = "k_tree"),
    new.reduction.name = "deng2021.5.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-deng-2021-5}
p.deng_2021.5 <-
  DimPlot(
    hypoth.query.deng_2021.5,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-5 transferred labels")

p1 + p.deng_2021.5 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-deng-2021-5-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.deng_2021.5 <-
  DimPlot(
    hypoth.query.deng_2021.5,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-5 transferred labels")

p.orig.deng_2021.5 <-
  DimPlot(
    hypoth.query.deng_2021.5,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Deng et al. 2021 batch-5 annotations")

p.deng_2021.5.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "deng2021.5.umap",
    group.by = "predicted.arc_deng_2021_5_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Deng et al. 2021 batch-5")

p.hypoth.deng_2021.5 +
  p.orig.deng_2021.5 +
  p.deng_2021.5.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.deng_2021.5,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "deng2021.5.umap")[,"deng20215umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.deng_2021.5,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "deng2021.5.umap")[,"deng20215umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.deng_2021.5,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "deng2021.5.umap")[,"deng20215umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.deng_2021.5,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "deng2021.5.umap")[,"deng20215umap_2"])))
    )
  )
```

## Mediobasal hypothalamus

### Rupp et al. 2021 10xV3

```{r transfer-ageing-rupp-2021-1}
hypoth.query.rupp_2021.1 <-
  hypoth.list[["Rupp10x_batch_1"]]
hypoth.anchors.rupp_2021.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.rupp_2021.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.rupp_2021.1 <-
  TransferData(
    anchorset = hypoth.anchors.rupp_2021.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.rupp_2021.1 <-
  MapQuery(
    anchorset = hypoth.anchors.rupp_2021.1,
    reference = combined_sct,
    query = hypoth.query.rupp_2021.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "hypoth.query.rupp_2021.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-rupp-2021-1-ageing}
rupp_2021.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.rupp_2021.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

rupp_2021.1.predictions.hypoth <-
  TransferData(
    anchorset = rupp_2021.1.anchors.hypoth,
    reference = hypoth.query.rupp_2021.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = rupp_2021.1.anchors.hypoth,
    reference = hypoth.query.rupp_2021.1,
    query = combined_sct,
    refdata = list(mbh_rupp_2021_1_mrt = "k_tree"),
    new.reduction.name = "rupp2021.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-rupp-2021-1}
p.rupp_2021.1 <-
  DimPlot(
    hypoth.query.rupp_2021.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Rupp et al. 2021 batch-1 transferred labels")

p1 + p.rupp_2021.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-rupp-2021-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.rupp_2021.1 <-
  DimPlot(
    hypoth.query.rupp_2021.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Rupp et al. 2021 batch-1 transferred labels")

p.orig.rupp_2021.1 <-
  DimPlot(
    hypoth.query.rupp_2021.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Rupp et al. 2021 batch-1 annotations")

p.rupp_2021.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "rupp2021.1.umap",
    group.by = "predicted.mbh_rupp_2021_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Rupp et al. 2021 batch-1")

p.hypoth.rupp_2021.1 +
  p.orig.rupp_2021.1 +
  p.rupp_2021.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.rupp_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "rupp2021.1.umap")[,"rupp20211umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.rupp_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "rupp2021.1.umap")[,"rupp20211umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.rupp_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "rupp2021.1.umap")[,"rupp20211umap_3"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.rupp_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "rupp2021.1.umap")[,"rupp20211umap_2"])))
    )
  )
```

## Ventromedial hypothalamus

### Affinati et al. 2021 10xV3 nuclei

```{r transfer-ageing-affinati-2021-1}
hypoth.query.affinati_2021.1 <-
  hypoth.list[["Affinati10x_batch_1"]]
hypoth.anchors.affinati_2021.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.affinati_2021.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.affinati_2021.1 <-
  TransferData(
    anchorset = hypoth.anchors.affinati_2021.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.affinati_2021.1 <-
  MapQuery(
    anchorset = hypoth.anchors.affinati_2021.1,
    reference = combined_sct,
    query = hypoth.query.affinati_2021.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.affinati_2021.1, filename = here(data_dir, "hypoth.query.affinati_2021.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-affinati-2021-1-ageing}
affinati_2021.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.affinati_2021.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

affinati_2021.1.predictions.hypoth <-
  TransferData(
    anchorset = affinati_2021.1.anchors.hypoth,
    reference = hypoth.query.affinati_2021.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = affinati_2021.1.anchors.hypoth,
    reference = hypoth.query.affinati_2021.1,
    query = combined_sct,
    refdata = list(vmh_affinati_2021_1_mrt = "k_tree"),
    new.reduction.name = "affinati2021.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-affinati-2021-1}
p.affinati_2021.1 <-
  DimPlot(
    hypoth.query.affinati_2021.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Query transferred labels")

p1 + p.affinati_2021.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-affinati-2021-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.affinati_2021.1 <-
  DimPlot(
    hypoth.query.affinati_2021.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-1 transferred labels")

p.orig.affinati_2021.1 <-
  DimPlot(
    hypoth.query.affinati_2021.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-1 annotations")

p.affinati_2021.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "affinati2021.1.umap",
    group.by = "predicted.vmh_affinati_2021_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Affinati et al. 2021 batch-1")

p.hypoth.affinati_2021.1 +
  p.orig.affinati_2021.1 +
  p.affinati_2021.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.affinati_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "affinati2021.1.umap")[,"affinati20211umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.affinati_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "affinati2021.1.umap")[,"affinati20211umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.affinati_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "affinati2021.1.umap")[,"affinati20211umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.affinati_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "affinati2021.1.umap")[,"affinati20211umap_2"])))
    )
  )
```

```{r transfer-ageing-affinati-2021-3}
hypoth.query.affinati_2021.3 <-
  hypoth.list[["Affinati10x_batch_3"]]
hypoth.anchors.affinati_2021.3 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.affinati_2021.3,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.affinati_2021.3 <-
  TransferData(
    anchorset = hypoth.anchors.affinati_2021.3,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.affinati_2021.3 <-
  MapQuery(
    anchorset = hypoth.anchors.affinati_2021.3,
    reference = combined_sct,
    query = hypoth.query.affinati_2021.3,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.affinati_2021.3, filename = here(data_dir, "hypoth.query.affinati_2021.3.h5Seurat"), overwrite = TRUE)
```

```{r transfer-affinati-2021-3-ageing}
affinati_2021.3.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.affinati_2021.3,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

affinati_2021.3.predictions.hypoth <-
  TransferData(
    anchorset = affinati_2021.3.anchors.hypoth,
    reference = hypoth.query.affinati_2021.3,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = affinati_2021.3.anchors.hypoth,
    reference = hypoth.query.affinati_2021.3,
    query = combined_sct,
    refdata = list(vmh_affinati_2021_3_mrt = "k_tree"),
    new.reduction.name = "affinati2021.3.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-affinati-2021-3}
p.affinati_2021.3 <-
  DimPlot(
    hypoth.query.affinati_2021.3,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-3 transferred labels")

p1 + p.affinati_2021.3 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-affinati-2021-3-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.affinati_2021.3 <-
  DimPlot(
    hypoth.query.affinati_2021.3,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-3 transferred labels")

p.orig.affinati_2021.3 <-
  DimPlot(
    hypoth.query.affinati_2021.3,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-3 annotations")

p.affinati_2021.3.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "affinati2021.3.umap",
    group.by = "predicted.vmh_affinati_2021_3_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Affinati et al. 2021 batch-3")

p.hypoth.affinati_2021.3 +
  p.orig.affinati_2021.3 +
  p.affinati_2021.3.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.affinati_2021.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "affinati2021.3.umap")[,"affinati20213umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.affinati_2021.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "affinati2021.3.umap")[,"affinati20213umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.affinati_2021.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "affinati2021.3.umap")[,"affinati20213umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.affinati_2021.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "affinati2021.3.umap")[,"affinati20213umap_2"])))
    )
  )
```

```{r transfer-ageing-affinati-2021-4}
hypoth.query.affinati_2021.4 <-
  hypoth.list[["Affinati10x_batch_4"]]
hypoth.anchors.affinati_2021.4 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.affinati_2021.4,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.affinati_2021.4 <-
  TransferData(
    anchorset = hypoth.anchors.affinati_2021.4,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.affinati_2021.4 <-
  MapQuery(
    anchorset = hypoth.anchors.affinati_2021.4,
    reference = combined_sct,
    query = hypoth.query.affinati_2021.4,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.affinati_2021.4, filename = here(data_dir, "hypoth.query.affinati_2021.4.h5Seurat"), overwrite = TRUE)
```

```{r transfer-affinati-2021-4-ageing}
affinati_2021.4.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.affinati_2021.4,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

affinati_2021.4.predictions.hypoth <-
  TransferData(
    anchorset = affinati_2021.4.anchors.hypoth,
    reference = hypoth.query.affinati_2021.4,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = affinati_2021.4.anchors.hypoth,
    reference = hypoth.query.affinati_2021.4,
    query = combined_sct,
    refdata = list(vmh_affinati_2021_4_mrt = "k_tree"),
    new.reduction.name = "affinati2021.4.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-affinati-2021-4}
p.affinati_2021.4 <-
  DimPlot(
    hypoth.query.affinati_2021.4,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-4 transferred labels")

p1 + p.affinati_2021.4 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-affinati-2021-4-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.affinati_2021.4 <-
  DimPlot(
    hypoth.query.affinati_2021.4,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-4 transferred labels")

p.orig.affinati_2021.4 <-
  DimPlot(
    hypoth.query.affinati_2021.4,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Affinati et al. 2021 batch-4 annotations")

p.affinati_2021.4.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "affinati2021.4.umap",
    group.by = "predicted.vmh_affinati_2021_4_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Affinati et al. 2021 batch-4")

p.hypoth.affinati_2021.4 +
  p.orig.affinati_2021.4 +
  p.affinati_2021.4.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.affinati_2021.4,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "affinati2021.4.umap")[,"affinati20214umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.affinati_2021.4,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "affinati2021.4.umap")[,"affinati20214umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.affinati_2021.4,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "affinati2021.4.umap")[,"affinati20214umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.affinati_2021.4,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "affinati2021.4.umap")[,"affinati20214umap_2"])))
    )
  )
```

### Kim et al. 2019 10xV2

```{r transfer-ageing-kim-2019-1}
hypoth.query.kim_2019.1 <-
  hypoth.list[["Kim10x_batch_1"]]
hypoth.anchors.kim_2019.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.kim_2019.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.kim_2019.1 <-
  TransferData(
    anchorset = hypoth.anchors.kim_2019.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.kim_2019.1 <-
  MapQuery(
    anchorset = hypoth.anchors.kim_2019.1,
    reference = combined_sct,
    query = hypoth.query.kim_2019.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.kim_2019.1, filename = here(data_dir, "hypoth.query.kim_2019.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-kim-2019-1-ageing}
kim_2019.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.kim_2019.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

kim_2019.1.predictions.hypoth <-
  TransferData(
    anchorset = kim_2019.1.anchors.hypoth,
    reference = hypoth.query.kim_2019.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = kim_2019.1.anchors.hypoth,
    reference = hypoth.query.kim_2019.1,
    query = combined_sct,
    refdata = list(vmh_kim_2019_1_mrt = "k_tree"),
    new.reduction.name = "kim2019.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-kim-2019-1}
p.kim_2019.1 <-
  DimPlot(
    hypoth.query.kim_2019.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Kim et al. 2019 transferred labels")

p1 + p.kim_2019.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-kim-2019-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.kim_2019.1 <-
  DimPlot(
    hypoth.query.kim_2019.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Kim et al. 2019 batch-1 transferred labels")

p.orig.kim_2019.1 <-
  DimPlot(
    hypoth.query.kim_2019.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Kim et al. 2019 batch-1 annotations")

p.kim_2019.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "kim2019.1.umap",
    group.by = "predicted.vmh_kim_2019_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Kim et al. 2019 batch-1")

p.hypoth.kim_2019.1 +
  p.orig.kim_2019.1 +
  p.kim_2019.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.kim_2019.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "kim2019.1.umap")[,"kim20191umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.kim_2019.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "kim2019.1.umap")[,"kim20191umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.kim_2019.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "kim2019.1.umap")[,"kim20191umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.kim_2019.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "kim2019.1.umap")[,"kim20191umap_2"])))
    )
  )
```

### Liu et al. 2022 10xV3

```{r transfer-ageing-liu-2022-1}
hypoth.query.liu_2022.1 <-
  hypoth.list[["Anderson10x_batch_1"]]
hypoth.anchors.liu_2022.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.liu_2022.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.liu_2022.1 <-
  TransferData(
    anchorset = hypoth.anchors.liu_2022.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.liu_2022.1 <-
  MapQuery(
    anchorset = hypoth.anchors.liu_2022.1,
    reference = combined_sct,
    query = hypoth.query.liu_2022.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.liu_2022.1, filename = here(data_dir, "hypoth.query.liu_2022.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-liu-2022-1-ageing}
liu_2022.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.liu_2022.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

liu_2022.1.predictions.hypoth <-
  TransferData(
    anchorset = liu_2022.1.anchors.hypoth,
    reference = hypoth.query.liu_2022.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = liu_2022.1.anchors.hypoth,
    reference = hypoth.query.liu_2022.1,
    query = combined_sct,
    refdata = list(vmhvl_liu_2022_1_mrt = "k_tree"),
    new.reduction.name = "liu2022.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-liu-2022-1}
p.liu_2022.1 <-
  DimPlot(
    hypoth.query.liu_2022.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Liu et al. 2022 batch-1 transferred labels")

p1 + p.liu_2022.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-liu-2022-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.liu_2022.1 <-
  DimPlot(
    hypoth.query.liu_2022.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Liu et al. 2022 batch-1 transferred labels")

p.orig.liu_2022.1 <-
  DimPlot(
    hypoth.query.liu_2022.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Liu et al. 2022 batch-1 annotations")

p.liu_2022.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "liu2022.1.umap",
    group.by = "predicted.vmhvl_liu_2022_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Liu et al. 2022 batch-1")

p.hypoth.liu_2022.1 +
  p.orig.liu_2022.1 +
  p.liu_2022.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.liu_2022.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "liu2022.1.umap")[,"liu20221umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.liu_2022.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "liu2022.1.umap")[,"liu20221umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.liu_2022.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "liu2022.1.umap")[,"liu20221umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.liu_2022.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "liu2022.1.umap")[,"liu20221umap_1"])))
    )
  )
```


## Ventroposterior hypothalamus

### Mickelsen et al. 2020 10xV2

```{r transfer-ageing-mickelsen-2020-1}
hypoth.query.mickelsen_2020.1 <-
  hypoth.list[["Flynn10x_batch_1"]]
hypoth.anchors.mickelsen_2020.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.mickelsen_2020.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.mickelsen_2020.1 <-
  TransferData(
    anchorset = hypoth.anchors.mickelsen_2020.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.mickelsen_2020.1 <-
  MapQuery(
    anchorset = hypoth.anchors.mickelsen_2020.1,
    reference = combined_sct,
    query = hypoth.query.mickelsen_2020.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.mickelsen_2020.1, filename = here(data_dir, "hypoth.query.mickelsen_2020.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-mickelsen-2020-1-ageing}
mickelsen_2020.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.mickelsen_2020.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

mickelsen_2020.1.predictions.hypoth <-
  TransferData(
    anchorset = mickelsen_2020.1.anchors.hypoth,
    reference = hypoth.query.mickelsen_2020.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = mickelsen_2020.1.anchors.hypoth,
    reference = hypoth.query.mickelsen_2020.1,
    query = combined_sct,
    refdata = list(vph_mickelsen_2020_1_mrt = "k_tree"),
    new.reduction.name = "mickelsen2020.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-mickelsen-2020-1}
p.mickelsen_2020.1 <-
  DimPlot(
    hypoth.query.mickelsen_2020.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Mickelsen et al. 2020 batch-1 transferred labels")

p1 + p.mickelsen_2020.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-mickelsen-2020-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.mickelsen_2020.1 <-
  DimPlot(
    hypoth.query.mickelsen_2020.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Mickelsen et al. 2020 batch-1 transferred labels")

p.orig.mickelsen_2020.1 <-
  DimPlot(
    hypoth.query.mickelsen_2020.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Mickelsen et al. 2020 batch-1 annotations")

p.mickelsen_2020.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "mickelsen2020.1.umap",
    group.by = "predicted.vph_mickelsen_2020_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Mickelsen et al. 2020 batch-1")

p.hypoth.mickelsen_2020.1 +
  p.orig.mickelsen_2020.1 +
  p.mickelsen_2020.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.mickelsen_2020.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "mickelsen2020.1.umap")[,"mickelsen20201umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.mickelsen_2020.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "mickelsen2020.1.umap")[,"mickelsen20201umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.mickelsen_2020.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "mickelsen2020.1.umap")[,"mickelsen20201umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.mickelsen_2020.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "mickelsen2020.1.umap")[,"mickelsen20201umap_2"])))
    )
  )
```

## Preoptic area

### Moffitt et al. 2018 10xV2

```{r transfer-ageing-moffitt-2018-1}
hypoth.query.moffitt_2018.1 <-
  hypoth.list[["Moffit10x_batch_1"]]
hypoth.anchors.moffitt_2018.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.moffitt_2018.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.moffitt_2018.1 <-
  TransferData(
    anchorset = hypoth.anchors.moffitt_2018.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.moffitt_2018.1 <-
  MapQuery(
    anchorset = hypoth.anchors.moffitt_2018.1,
    reference = combined_sct,
    query = hypoth.query.moffitt_2018.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.moffitt_2018.1, filename = here(data_dir, "hypoth.query.moffitt_2018.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-moffitt-2018-1-ageing}
moffitt_2018.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.moffitt_2018.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

moffitt_2018.1.predictions.hypoth <-
  TransferData(
    anchorset = moffitt_2018.1.anchors.hypoth,
    reference = hypoth.query.moffitt_2018.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = moffitt_2018.1.anchors.hypoth,
    reference = hypoth.query.moffitt_2018.1,
    query = combined_sct,
    refdata = list(poa_moffitt_2018_1_mrt = "k_tree"),
    new.reduction.name = "moffitt2018.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-moffitt-2018-1}
p.moffitt_2018.1 <-
  DimPlot(
    hypoth.query.moffitt_2018.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-1 transferred labels")

p1 + p.moffitt_2018.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-moffitt-2018-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.moffitt_2018.1 <-
  DimPlot(
    hypoth.query.moffitt_2018.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-1 transferred labels")

p.orig.moffitt_2018.1 <-
  DimPlot(
    hypoth.query.moffitt_2018.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-1 annotations")

p.moffitt_2018.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "moffitt2018.1.umap",
    group.by = "predicted.poa_moffitt_2018_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Moffitt et al. 2018 batch-1")

p.hypoth.moffitt_2018.1 +
  p.orig.moffitt_2018.1 +
  p.moffitt_2018.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.moffitt_2018.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "moffitt2018.1.umap")[,"moffitt20181umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.moffitt_2018.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "moffitt2018.1.umap")[,"moffitt20181umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.moffitt_2018.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "moffitt2018.1.umap")[,"moffitt20181umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.moffitt_2018.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "moffitt2018.1.umap")[,"moffitt20181umap_2"])))
    )
  )
```

```{r transfer-ageing-moffitt-2018-2}
hypoth.query.moffitt_2018.2 <-
  hypoth.list[["Moffit10x_batch_2"]]
hypoth.anchors.moffitt_2018.2 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.moffitt_2018.2,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.moffitt_2018.2 <-
  TransferData(
    anchorset = hypoth.anchors.moffitt_2018.2,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.moffitt_2018.2 <-
  MapQuery(
    anchorset = hypoth.anchors.moffitt_2018.2,
    reference = combined_sct,
    query = hypoth.query.moffitt_2018.2,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.moffitt_2018.2, filename = here(data_dir, "hypoth.query.moffitt_2018.2.h5Seurat"), overwrite = TRUE)
```

```{r transfer-moffitt-2018-2-ageing}
moffitt_2018.2.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.moffitt_2018.2,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

moffitt_2018.2.predictions.hypoth <-
  TransferData(
    anchorset = moffitt_2018.2.anchors.hypoth,
    reference = hypoth.query.moffitt_2018.2,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = moffitt_2018.2.anchors.hypoth,
    reference = hypoth.query.moffitt_2018.2,
    query = combined_sct,
    refdata = list(poa_moffitt_2018_2_mrt = "k_tree"),
    new.reduction.name = "moffitt2018.2.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-moffitt-2018-2}
p.moffitt_2018.2 <-
  DimPlot(
    hypoth.query.moffitt_2018.2,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Query transferred labels")

p1 + p.moffitt_2018.2 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-moffitt-2018-2-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.moffitt_2018.2 <-
  DimPlot(
    hypoth.query.moffitt_2018.2,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-2 transferred labels")

p.orig.moffitt_2018.2 <-
  DimPlot(
    hypoth.query.moffitt_2018.2,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-2 annotations")

p.moffitt_2018.2.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "moffitt2018.2.umap",
    group.by = "predicted.poa_moffitt_2018_2_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Moffitt et al. 2018 batch-2")

p.hypoth.moffitt_2018.2 +
  p.orig.moffitt_2018.2 +
  p.moffitt_2018.2.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.moffitt_2018.2,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "moffitt2018.2.umap")[,"moffitt20182umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.moffitt_2018.2,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "moffitt2018.2.umap")[,"moffitt20182umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.moffitt_2018.2,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "moffitt2018.2.umap")[,"moffitt20182umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.moffitt_2018.2,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "moffitt2018.2.umap")[,"moffitt20182umap_2"])))
    )
  )
```

```{r transfer-ageing-moffitt-2018-3}
hypoth.query.moffitt_2018.3 <-
  hypoth.list[["Moffit10x_batch_3"]]
hypoth.anchors.moffitt_2018.3 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.moffitt_2018.3,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.moffitt_2018.3 <-
  TransferData(
    anchorset = hypoth.anchors.moffitt_2018.3,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.moffitt_2018.3 <-
  MapQuery(
    anchorset = hypoth.anchors.moffitt_2018.3,
    reference = combined_sct,
    query = hypoth.query.moffitt_2018.3,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.moffitt_2018.3, filename = here(data_dir, "hypoth.query.moffitt_2018.3.h5Seurat"), overwrite = TRUE)
```

```{r transfer-moffitt-2018-3-ageing}
moffitt_2018.3.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.moffitt_2018.3,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

moffitt_2018.3.predictions.hypoth <-
  TransferData(
    anchorset = moffitt_2018.3.anchors.hypoth,
    reference = hypoth.query.moffitt_2018.3,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = moffitt_2018.3.anchors.hypoth,
    reference = hypoth.query.moffitt_2018.3,
    query = combined_sct,
    refdata = list(poa_moffitt_2018_3_mrt = "k_tree"),
    new.reduction.name = "moffitt2018.3.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-moffitt-2018-3}
p.moffitt_2018.3 <-
  DimPlot(
    hypoth.query.moffitt_2018.3,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Query transferred labels")

p1 + p.moffitt_2018.3 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-moffitt-2018-3-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.moffitt_2018.3 <-
  DimPlot(
    hypoth.query.moffitt_2018.3,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-3 transferred labels")

p.orig.moffitt_2018.3 <-
  DimPlot(
    hypoth.query.moffitt_2018.3,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Moffitt et al. 2018 batch-3 annotations")

p.moffitt_2018.3.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "moffitt2018.3.umap",
    group.by = "predicted.poa_moffitt_2018_3_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Moffitt et al. 2018 batch-3")

p.hypoth.moffitt_2018.3 +
  p.orig.moffitt_2018.3 +
  p.moffitt_2018.3.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.moffitt_2018.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "moffitt2018.3.umap")[,"moffitt20183umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.moffitt_2018.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "moffitt2018.3.umap")[,"moffitt20183umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.moffitt_2018.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "moffitt2018.3.umap")[,"moffitt20183umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.moffitt_2018.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "moffitt2018.3.umap")[,"moffitt20183umap_2"])))
    )
  )
```

## Suprachiasmatic nucleus

### Wen et al. 2020 10xV2

```{r transfer-ageing-wen-2020-1}
hypoth.query.wen_2020.1 <-
  hypoth.list[["wen10x_batch_1"]]
hypoth.anchors.wen_2020.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.wen_2020.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.wen_2020.1 <-
  TransferData(
    anchorset = hypoth.anchors.wen_2020.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.wen_2020.1 <-
  MapQuery(
    anchorset = hypoth.anchors.wen_2020.1,
    reference = combined_sct,
    query = hypoth.query.wen_2020.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "hypoth.query.wen_2020.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-wen-2020-1-ageing}
wen_2020.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.wen_2020.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

wen_2020.1.predictions.hypoth <-
  TransferData(
    anchorset = wen_2020.1.anchors.hypoth,
    reference = hypoth.query.wen_2020.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = wen_2020.1.anchors.hypoth,
    reference = hypoth.query.wen_2020.1,
    query = combined_sct,
    refdata = list(scn_wen_2020_1_mrt = "k_tree"),
    new.reduction.name = "wen2020.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-wen-2020-1}
p.wen_2020.1 <-
  DimPlot(
    hypoth.query.wen_2020.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Wen et al. 2020 10xV2 transferred labels")

p1 + p.wen_2020.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-wen-2020-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.wen_2020.1 <-
  DimPlot(
    hypoth.query.wen_2020.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Wen et al. 2020 10xV2 batch-1 transferred labels")

p.orig.wen_2020.1 <-
  DimPlot(
    hypoth.query.wen_2020.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Wen et al. 2020 10xV2 batch-1 annotations")

p.wen_2020.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "wen2020.1.umap",
    group.by = "predicted.scn_wen_2020_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Wen et al. 2020 10xV2 batch-1")

p.hypoth.wen_2020.1 +
  p.orig.wen_2020.1 +
  p.wen_2020.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.wen_2020.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "wen2020.1.umap")[,"wen20201umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.wen_2020.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "wen2020.1.umap")[,"wen20201umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.wen_2020.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "wen2020.1.umap")[,"wen20201umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.wen_2020.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "wen2020.1.umap")[,"wen20201umap_2"])))
    )
  )
```

### Wen et al. 2020 Dropseq

```{r transfer-ageing-wen-2020-2}
hypoth.query.wen_2020.2 <-
  hypoth.list[["wenDropseq_batch_1"]]
hypoth.anchors.wen_2020.2 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.wen_2020.2,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.wen_2020.2 <-
  TransferData(
    anchorset = hypoth.anchors.wen_2020.2,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.wen_2020.2 <-
  MapQuery(
    anchorset = hypoth.anchors.wen_2020.2,
    reference = combined_sct,
    query = hypoth.query.wen_2020.2,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.wen_2020.2, filename = here(data_dir, "hypoth.query.wen_2020.2.h5Seurat"), overwrite = TRUE)
```

```{r transfer-wen-2020-2-ageing}
wen_2020.2.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.wen_2020.2,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

wen_2020.2.predictions.hypoth <-
  TransferData(
    anchorset = wen_2020.2.anchors.hypoth,
    reference = hypoth.query.wen_2020.2,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = wen_2020.2.anchors.hypoth,
    reference = hypoth.query.wen_2020.2,
    query = combined_sct,
    refdata = list(scn_wen_2020_2_mrt = "k_tree"),
    new.reduction.name = "wen2020.2.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-wen-2020-2}
p.wen_2020.2 <-
  DimPlot(
    hypoth.query.wen_2020.2,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Wen et al. 2020 Dropseq transferred labels")

p1 + p.wen_2020.2 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-wen-2020-2-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.wen_2020.2 <-
  DimPlot(
    hypoth.query.wen_2020.2,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Wen et al. 2020 Dropseq batch-2 transferred labels")

p.orig.wen_2020.2 <-
  DimPlot(
    hypoth.query.wen_2020.2,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Wen et al. 2020 Dropseq batch-2 annotations")

p.wen_2020.2.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "wen2020.2.umap",
    group.by = "predicted.scn_wen_2020_2_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Wen et al. 2020 Dropseq batch-2")

p.hypoth.wen_2020.2 +
  p.orig.wen_2020.2 +
  p.wen_2020.2.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.wen_2020.2,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "wen2020.2.umap")[,"wen20202umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.wen_2020.2,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "wen2020.2.umap")[,"wen20202umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.wen_2020.2,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "wen2020.2.umap")[,"wen20202umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.wen_2020.2,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "wen2020.2.umap")[,"wen20202umap_2"])))
    )
  )
```

### Morris et al. 2021 10xV3

```{r transfer-ageing-morris-2021-1}
hypoth.query.morris_2021.1 <-
  hypoth.list[["Morris10x_batch_1"]]
hypoth.anchors.morris_2021.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.morris_2021.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.morris_2021.1 <-
  TransferData(
    anchorset = hypoth.anchors.morris_2021.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.morris_2021.1 <-
  MapQuery(
    anchorset = hypoth.anchors.morris_2021.1,
    reference = combined_sct,
    query = hypoth.query.morris_2021.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.morris_2021.1, filename = here(data_dir, "hypoth.query.morris_2021.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-morris-2021-1-ageing}
morris_2021.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.morris_2021.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

morris_2021.1.predictions.hypoth <-
  TransferData(
    anchorset = morris_2021.1.anchors.hypoth,
    reference = hypoth.query.morris_2021.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = morris_2021.1.anchors.hypoth,
    reference = hypoth.query.morris_2021.1,
    query = combined_sct,
    refdata = list(scn_morris_2021_1_mrt = "k_tree"),
    new.reduction.name = "morris2021.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-morris-2021-1}
p.morris_2021.1 <-
  DimPlot(
    hypoth.query.morris_2021.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-1 transferred labels")

p1 + p.morris_2021.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-morris-2021-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.morris_2021.1 <-
  DimPlot(
    hypoth.query.morris_2021.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-1 transferred labels")

p.orig.morris_2021.1 <-
  DimPlot(
    hypoth.query.morris_2021.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-1 annotations")

p.morris_2021.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "morris2021.1.umap",
    group.by = "predicted.scn_morris_2021_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Morris et al. 2021 batch-1")

p.hypoth.morris_2021.1 +
  p.orig.morris_2021.1 +
  p.morris_2021.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.morris_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "morris2021.1.umap")[,"morris20211umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.morris_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "morris2021.1.umap")[,"morris20211umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.morris_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "morris2021.1.umap")[,"morris20211umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.morris_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "morris2021.1.umap")[,"morris20211umap_2"])))
    )
  )
```

```{r transfer-ageing-morris-2021-2}
hypoth.query.morris_2021.2 <-
  hypoth.list[["Morris10x_batch_2"]]
hypoth.anchors.morris_2021.2 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.morris_2021.2,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.morris_2021.2 <-
  TransferData(
    anchorset = hypoth.anchors.morris_2021.2,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.morris_2021.2 <-
  MapQuery(
    anchorset = hypoth.anchors.morris_2021.2,
    reference = combined_sct,
    query = hypoth.query.morris_2021.2,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.morris_2021.2, filename = here(data_dir, "hypoth.query.morris_2021.2.h5Seurat"), overwrite = TRUE)
```

```{r transfer-morris-2021-2-ageing}
morris_2021.2.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.morris_2021.2,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

morris_2021.2.predictions.hypoth <-
  TransferData(
    anchorset = morris_2021.2.anchors.hypoth,
    reference = hypoth.query.morris_2021.2,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = morris_2021.2.anchors.hypoth,
    reference = hypoth.query.morris_2021.2,
    query = combined_sct,
    refdata = list(scn_morris_2021_2_mrt = "k_tree"),
    new.reduction.name = "morris2021.2.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-morris-2021-2}
p.morris_2021.2 <-
  DimPlot(
    hypoth.query.morris_2021.2,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-1 transferred labels")

p1 + p.morris_2021.2 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-morris-2021-2-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.morris_2021.2 <-
  DimPlot(
    hypoth.query.morris_2021.2,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-2 transferred labels")

p.orig.morris_2021.2 <-
  DimPlot(
    hypoth.query.morris_2021.2,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-2 annotations")

p.morris_2021.2.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "morris2021.2.umap",
    group.by = "predicted.scn_morris_2021_2_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Morris et al. 2021 batch-2")

p.hypoth.morris_2021.2 +
  p.orig.morris_2021.2 +
  p.morris_2021.2.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.morris_2021.2,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "morris2021.2.umap")[,"morris20212umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.morris_2021.2,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "morris2021.2.umap")[,"morris20212umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.morris_2021.2,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "morris2021.2.umap")[,"morris20212umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.morris_2021.2,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "morris2021.2.umap")[,"morris20212umap_2"])))
    )
  )
```

```{r transfer-ageing-morris-2021-3}
hypoth.query.morris_2021.3 <-
  hypoth.list[["Morris10x_batch_3"]]
hypoth.anchors.morris_2021.3 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.morris_2021.3,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.morris_2021.3 <-
  TransferData(
    anchorset = hypoth.anchors.morris_2021.3,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.morris_2021.3 <-
  MapQuery(
    anchorset = hypoth.anchors.morris_2021.3,
    reference = combined_sct,
    query = hypoth.query.morris_2021.3,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.morris_2021.3, filename = here(data_dir, "hypoth.query.morris_2021.3.h5Seurat"), overwrite = TRUE)
```

```{r transfer-morris-2021-3-ageing}
morris_2021.3.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.morris_2021.3,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

morris_2021.3.predictions.hypoth <-
  TransferData(
    anchorset = morris_2021.3.anchors.hypoth,
    reference = hypoth.query.morris_2021.3,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = morris_2021.3.anchors.hypoth,
    reference = hypoth.query.morris_2021.3,
    query = combined_sct,
    refdata = list(scn_morris_2021_3_mrt = "k_tree"),
    new.reduction.name = "morris2021.3.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-morris-2021-3}
p.morris_2021.3 <-
  DimPlot(
    hypoth.query.morris_2021.3,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-1 transferred labels")

p1 + p.morris_2021.3 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-morris-2021-3-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.morris_2021.3 <-
  DimPlot(
    hypoth.query.morris_2021.3,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-3 transferred labels")

p.orig.morris_2021.3 <-
  DimPlot(
    hypoth.query.morris_2021.3,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Morris et al. 2021 batch-3 annotations")

p.morris_2021.3.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "morris2021.3.umap",
    group.by = "predicted.scn_morris_2021_3_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Morris et al. 2021 batch-3")

p.hypoth.morris_2021.3 +
  p.orig.morris_2021.3 +
  p.morris_2021.3.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.morris_2021.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "morris2021.3.umap")[,"morris20213umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.morris_2021.3,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "morris2021.3.umap")[,"morris20213umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.morris_2021.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "morris2021.3.umap")[,"morris20213umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.morris_2021.3,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "morris2021.3.umap")[,"morris20213umap_2"])))
    )
  )
```

## Lateral hypothalamic area

### Mickelsen et al. 2019 10xV2

```{r transfer-ageing-mickelsen-2019-1}
hypoth.query.mickelsen_2019.1 <-
  hypoth.list[["Mickelsen10x_batch_1"]]
hypoth.anchors.mickelsen_2019.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.mickelsen_2019.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.mickelsen_2019.1 <-
  TransferData(
    anchorset = hypoth.anchors.mickelsen_2019.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.mickelsen_2019.1 <-
  MapQuery(
    anchorset = hypoth.anchors.mickelsen_2019.1,
    reference = combined_sct,
    query = hypoth.query.mickelsen_2019.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.mickelsen_2019.1, filename = here(data_dir, "hypoth.query.mickelsen_2019.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-mickelsen-2019-1-ageing}
mickelsen_2019.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.mickelsen_2019.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

mickelsen_2019.1.predictions.hypoth <-
  TransferData(
    anchorset = mickelsen_2019.1.anchors.hypoth,
    reference = hypoth.query.mickelsen_2019.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = mickelsen_2019.1.anchors.hypoth,
    reference = hypoth.query.mickelsen_2019.1,
    query = combined_sct,
    refdata = list(lha_mickelsen_2019_1_mrt = "k_tree"),
    new.reduction.name = "mickelsen2019.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-mickelsen-2019-1}
p.mickelsen_2019.1 <-
  DimPlot(
    hypoth.query.mickelsen_2019.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Mickelsen et al. 2019 batch-1 transferred labels")

p1 + p.mickelsen_2019.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-mickelsen-2019-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.mickelsen_2019.1 <-
  DimPlot(
    hypoth.query.mickelsen_2019.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Mickelsen et al. 2019 batch-1 transferred labels")

p.orig.mickelsen_2019.1 <-
  DimPlot(
    hypoth.query.mickelsen_2019.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Mickelsen et al. 2019 batch-1 annotations")

p.mickelsen_2019.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "mickelsen2019.1.umap",
    group.by = "predicted.lha_mickelsen_2019_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Mickelsen et al. 2019 batch-1")

p.hypoth.mickelsen_2019.1 +
  p.orig.mickelsen_2019.1 +
  p.mickelsen_2019.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.mickelsen_2019.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "mickelsen2019.1.umap")[,"mickelsen20191umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.mickelsen_2019.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "mickelsen2019.1.umap")[,"mickelsen20191umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.mickelsen_2019.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "mickelsen2019.1.umap")[,"mickelsen20191umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.mickelsen_2019.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "mickelsen2019.1.umap")[,"mickelsen20191umap_2"])))
    )
  )
```


### Rossi et al. 2019 Dropseq

```{r transfer-ageing-rossi-2019-1}
hypoth.query.rossi_2019.1 <-
  hypoth.list[["Mickelsen10x_batch_1"]]
hypoth.anchors.rossi_2019.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.rossi_2019.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.rossi_2019.1 <-
  TransferData(
    anchorset = hypoth.anchors.rossi_2019.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.rossi_2019.1 <-
  MapQuery(
    anchorset = hypoth.anchors.rossi_2019.1,
    reference = combined_sct,
    query = hypoth.query.rossi_2019.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.rossi_2019.1, filename = here(data_dir, "hypoth.query.rossi_2019.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-rossi-2019-1-ageing}
rossi_2019.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.rossi_2019.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

rossi_2019.1.predictions.hypoth <-
  TransferData(
    anchorset = rossi_2019.1.anchors.hypoth,
    reference = hypoth.query.rossi_2019.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = rossi_2019.1.anchors.hypoth,
    reference = hypoth.query.rossi_2019.1,
    query = combined_sct,
    refdata = list(lha_rossi_2019_1_mrt = "k_tree"),
    new.reduction.name = "rossi2019.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-rossi-2019-1}
p.rossi_2019.1 <-
  DimPlot(
    hypoth.query.rossi_2019.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Rossi et al. 2019 Dropseq transferred labels")

p1 + p.rossi_2019.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-rossi-2019-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.rossi_2019.1 <-
  DimPlot(
    hypoth.query.rossi_2019.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Rossi et al. 2019 Dropseq batch-1 transferred labels")

p.orig.rossi_2019.1 <-
  DimPlot(
    hypoth.query.rossi_2019.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Rossi et al. 2019 Dropseq batch-1 annotations")

p.rossi_2019.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "rossi2019.1.umap",
    group.by = "predicted.lha_rossi_2019_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Rossi et al. 2019 Dropseq")

p.hypoth.rossi_2019.1 +
  p.orig.rossi_2019.1 +
  p.rossi_2019.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.rossi_2019.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "rossi2019.1.umap")[,"rossi20191umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.rossi_2019.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "rossi2019.1.umap")[,"rossi20191umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.rossi_2019.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "rossi2019.1.umap")[,"rossi20191umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.rossi_2019.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "rossi2019.1.umap")[,"rossi20191umap_2"])))
    )
  )
```

### Paraventricular nucleus

```{r transfer-ageing-lopez-2021-1}
DefaultAssay(hypoth.list[["Lopez_2021_10xv3"]]) <- "SCT"
hypoth.query.lopez_2021.1 <-
  hypoth.list[["Lopez_2021_10xv3"]]
hypoth.anchors.lopez_2021.1 <-
  FindTransferAnchors(
    reference = combined_sct,
    query = hypoth.query.lopez_2021.1,
    normalization.method = "SCT",
    dims = 1:npcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

predictions.lopez_2021.1 <-
  TransferData(
    anchorset = hypoth.anchors.lopez_2021.1,
    refdata = combined_sct$k_tree,
    dims = 1:npcs)

hypoth.query.lopez_2021.1 <-
  MapQuery(
    anchorset = hypoth.anchors.lopez_2021.1,
    reference = combined_sct,
    query = hypoth.query.lopez_2021.1,
    refdata = list(k_tree = "k_tree"),
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(hypoth.query.lopez_2021.1, filename = here(data_dir, "hypoth.query.lopez_2021.1.h5Seurat"), overwrite = TRUE)
```

```{r transfer-lopez-2021-1-ageing}
lopez_2021.1.anchors.hypoth <-
  FindTransferAnchors(
    reference = hypoth.query.lopez_2021.1,
    query = combined_sct,
    normalization.method = "SCT",
    dims = 1:n_pcs,
    k.anchor = 10,
    k.score = 50,
    k.filter = 100,
    max.features = 500,
    n.trees = 100,
    reference.reduction = "pca")

lopez_2021.1.predictions.hypoth <-
  TransferData(
    anchorset = lopez_2021.1.anchors.hypoth,
    reference = hypoth.query.lopez_2021.1,
    refdata = "k_tree",
    dims = 1:n_pcs)

combined_sct <-
  MapQuery(
    anchorset = lopez_2021.1.anchors.hypoth,
    reference = hypoth.query.lopez_2021.1,
    query = combined_sct,
    refdata = list(pvn_lopez_2021_1_mrt = "k_tree"),
    new.reduction.name = "lopez2021.1.umap",
    reference.reduction = "pca",
    reduction.model = "umap")
SaveH5Seurat(combined_sct, filename = here(data_dir, "webb_astrocytes_combined_sct.h5Seurat"), overwrite = TRUE)
```

```{r pl-transfer-ageing-lopez-2021-1}
p.lopez_2021.1 <-
  DimPlot(
    hypoth.query.lopez_2021.1,
    reduction = "ref.umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE) +
  NoLegend() +
  ggtitle("Lopez et al. 2021 transferred labels")

p1 + p.lopez_2021.1 & scale_x_continuous(
  limits = c(
    floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_1"]))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"])),
    ceiling(max(
      Embeddings(combined_sct,
                 "umap")[,"UMAP_2"]))
    )
  )
```

```{r pl-transfer-lopez-2021-1-ageing, fig.asp=0.206, fig.width = 16}
p.hypoth.lopez_2021.1 <-
  DimPlot(
    hypoth.query.lopez_2021.1,
    reduction = "umap",
    group.by = "predicted.k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Lopez et al. 2021 batch-1 transferred labels")

p.orig.lopez_2021.1 <-
  DimPlot(
    hypoth.query.lopez_2021.1,
    reduction = "umap",
    group.by = "k_tree",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Lopez et al. 2021 batch-1 annotations")

p.lopez_2021.1.hypoth <-
  DimPlot(
    combined_sct,
    reduction = "lopez2021.1.umap",
    group.by = "predicted.pvn_lopez_2021_1_mrt",
    label = TRUE,
    label.size = 3,
    pt.size = 5,
    repel = TRUE
  ) +
  NoLegend() +
  ggtitle("Reference backward-transferred labels from Lopez et al. 2021 batch-1")

p.hypoth.lopez_2021.1 +
  p.orig.lopez_2021.1 +
  p.lopez_2021.1.hypoth & scale_x_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.lopez_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "lopez2021.1.umap")[,"lopez20211umap_1"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.lopez_2021.1,
                   "umap")[,"UMAP_1"],
        Embeddings(combined_sct,
                   "lopez2021.1.umap")[,"lopez20211umap_1"])))
    )
  ) & scale_y_continuous(
    limits = c(
      floor(min(c(
        Embeddings(hypoth.query.lopez_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "lopez2021.1.umap")[,"lopez20211umap_2"]))),
      ceiling(max(c(
        Embeddings(hypoth.query.lopez_2021.1,
                   "umap")[,"UMAP_2"],
        Embeddings(combined_sct,
                   "lopez2021.1.umap")[,"lopez20211umap_2"])))
    )
  )
```

```{r save}
save.image("transfers.RData")
```


